Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-20 paper-ieee-trans.tex

{\sl DataGrid - Research and Technological Development for an International Data Grid} project 
has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
FP5-IST - Programme for research, technological development and demonstration on a "User--friendly information society, 1998-2002" (IST--2000--25182E)

{\sl EGEE - Enabling grids For E--science} project
has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
 FP6-INFRASTRUCTURES - Research infrastructures: Specific programme for research, technological development and demonstration: "Structuring the European Research Area" under the Sixth Framework Programme 2002-2006, (INFSO--RI--508833)

{\sl EGEE - Enabling grids For E--science--II} project
 has received funding from the European Commission - Community Research and Development Information System (CORDIS) under 
 FP6-2005-INFRASTRUCTURES-7 programme, Topic - "INFRASTR-3 - Communication network development in conjunction with thematic priority 2 (Information Society Technologies) to establish a high--capacity and high--speed communications network for all researchers in Europe (GEANT)", (INFSO--RI--031688)

{\sl EGEE - Enabling grids For E--science--III} project
  has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
  FP7-INFRASTRUCTURES - Specific Programme "Capacities": Research infrastructures, Topic - "INFRA-2007-1.2-03 - e--Science Grid infrastructures", (INFSO--RI--222667)

{\sl INDIGO--DataCloud} project has received funding from the European Research
Council (ERC) under the European Union's Horizon 2020 research and innovation
programme (GA--777536).

>>>>

%{\sl DataGrid - Research and Technological Development for an International Data Grid} project 
%has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
%FP5-IST - Programme for research, technological development and demonstration on a "User--friendly information society, 1998-2002" (IST--2000--25182E)
%{\sl EGEE - Enabling grids For E--science} project
%has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
% FP6-INFRASTRUCTURES - Research infrastructures: Specific programme for research, technological development and demonstration: "Structuring the European Research Area" under the Sixth Framework Programme 2002-2006, (INFSO--RI--508833)
%{\sl EGEE - Enabling grids For E--science--II} project
% has received funding from the European Commission - Community Research and Development Information System (CORDIS) under 
% FP6-2005-INFRASTRUCTURES-7 programme, Topic - "INFRASTR-3 - Communication network development in conjunction with thematic priority 2 (Information Society Technologies) to establish a high--capacity and high--speed communications network for all researchers in Europe (GEANT)", (INFSO--RI--031688)
%{\sl EGEE - Enabling grids For E--science--III} project has received funding from the European Commission - Community Research and Development Information System (CORDIS) under
%  FP7-INFRASTRUCTURES - Specific Programme "Capacities": Research infrastructures, Topic - "INFRA-2007-1.2-03 - e--Science Grid infrastructures", (INFSO--RI--222667)

{\sl DataGrid - Research and Technological Development for an International Data Grid} project has received funding from the European Union's Fifth Framework Programme under grant agreement IST--2000--25182E.

{\sl EGEE - Enabling grids For E--science} project has received funding from the European Union's Sixth Framework Programme under grant agreement INFSO--RI--508833.

{\sl EGEE - Enabling grids For E--science--II} project has received funding from the European Union's Sixth Framework Programme under grant agreement INFSO--RI--031688.

{\sl EGEE - Enabling grids For E--science--III} project has received funding from the European Union's Seventh Framework Programme under grant agreement INFSO--RI--222667.

{\sl ETICS - E--Infrastructure for Testing, Integration and Configuration of Software} project has received funding from the European Union's Sixth Framework Programme under grant agreement INFSO--RI--026753.

{\sl ETICS - E--Infrastructure for Testing, Integration and Configuration of Software - Phase 2} project has received funding from the European Union's Seventh Framework Programme under grant agreement INFSO--RI--223782.

{\sl EGI--InSPIRE - European Grid Initiative: Integrated Sustainable Pan--European Infrastructure for Researchers in Europe} project has received funding from the European Union's Seventh Framework Programme under grant agreement INFSO--RI--261323.

{\sl EGI--Engage} project has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement RIA--654142.

{\sl INDIGO--DataCloud} project has received funding from the European Union's Horizon 2020 research and innovation programme under grant agreement RIA--653549.
